Locally Conservative Discontinuous Petrov-Galerkin Finite Elements for Fluid Problems

### 2013-06-07 docs/Truman/LocalConservation/paper/paper.tex
Rewrite of results for Local Conservation paper.

The optimal test functions are determined by solving local problems determined
by the choice of test norm. For illustrative purposes we choose the robust
test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
choice, we get our local problem:

@@

\section{Numerical Experiments}
We explore each of the following experiments with two sets of test norms: the
standard graph norm, and the aforementioned robust norm.

\subsection{Erickson-Johnson Model Problem}
The Erickson-Johnson problem is one of the few convection-diffusion problems
with a known analytical solution. Take a domain $\Omega=[0,1]^2$, with
$\bbeta=(1,0)^T$, $f=0$ and boundary conditions $\hat t=u_0$ when
$\beta_n\le0$, and $u_0$ is the trace of the exact solution. For
$n=1,2,\cdots$, let
$\lambda_n=n^2*\pi^2*\epsilon$,
$r_n=\frac{1+\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, and 
$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, the exact solution
is
\begin{equation}
u(x,y)=C_0+\sum_{n=1}^\infty C_n\frac{\exp(s_n(x-1))-\exp(r_n(x-1))}
{r_n\exp(-s_n)-s_n\exp(-s_n)}\cos(n\pi y)\,.
\label{eq:ericksonExact}
\end{equation}
Taking $\epsilon=0.01$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
like Figure \ref{fig:erickson}. We solve this problem with both conservative
and nonconservative formulations of DPG with both graph and robust test norms.

\begin{figure}[h!]
\centering
\includegraphics[width=0.6\textwidth]{figs/Erickson/exact.png}
\caption{Erickson-Johnson exact solution}
\label{fig:erickson}
\end{figure}

We plot the $L^2$ and energy error for the various methods in Figures
\ref{fig:ericksonGraphError} and \ref{fig:ericksonRobustError}. Encouragingly,
the conservative and nonconservative plots appear to lay right on top of each
other. This indicates that the conservative formulation at least doensn't hurt
our convergence significantly.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/graphError.pdf}
\caption{With graph norm}
\label{fig:ericksonGraphError}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/robustError.pdf}
\caption{With robust norm}
\label{fig:ericksonRobustError}
\end{subfigure}
\caption{Error in Erickson-Johnson solutions}
\end{figure}

We plot the flux imbalance errors in Figures \ref{fig:ericksonGraphFlux} and
\ref{fig:ericksonRobustFlux}. As expected, the element conservative
formulation brings these errors to the order of machine precision, but it is
worth pointing out that the flux imbalances for standard DPG are reasonable,
especially under refinement.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/graphFlux.pdf}
\caption{With graph norm}
\label{fig:ericksonGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Erickson/robustFlux.pdf}
\caption{With robust norm}
\label{fig:ericksonRobustFlux}
\end{subfigure}
\caption{Flux imbalance in Erickson-Johnson solutions}
\end{figure}

\subsection{Skewed Convection-Diffusion Problem}
This is a standard convection-diffusion problem with a skewed convection
vector relative to the mesh. The problem setup is identical to the
Erickson-Johnson problems except that $\bbeta=(2,1)$. The following results
are for $\epsilon=10^{-4}$.

On our initial mesh, we see no noticeable difference between conservative and
nonconservative results, though the choice of test norm affects things
dramatically. The graph norm produces a solution which is comparable to an L2
project of the exact solution. In this case, the field variable don't show the
very small boundary layer along the right and top surfaces, though a
visualization of the traces would show that the wall boundary condition is in
fact being enforced. As we refine, the field variables will begin to reflect
the boundary layer. On the other hand, the robust norm does show a boundary
layer being formed in the field variables.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/graph0c.png}
\caption{Conservative with graph norm}
\label{fig:confusionGraph0c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/robust0c.png}
\caption{Conservative with robust norm}
\label{fig:confusionRobust0c}
\end{subfigure}
\caption{Skewed convection-diffusion problem with initial mesh}
\end{figure}

As we refine, the three results, nonconservative with graph or robust norm,
and conservative with graph norm converge to a an essentially identical
solution (to the eyeball norm), as represented by
Figure~\ref{fig:confusionGraph8c}.

% However, the conservative formulation with
% the robust norm seems to exhibit some noise at the right wall as seen in
% Figure~\ref{fig:confusionRobust8c}.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/graph8c.png}
\includegraphics[width=\textwidth]{figs/Confusion/graph8c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:confusionGraph8c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/robust8c.png}
\includegraphics[width=\textwidth]{figs/Confusion/robust8c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:confusionRobust8c}
\end{subfigure}
\caption{Skewed convection-diffusion problem after 8 refinements}
\end{figure}

% If we zoom in on one of the noisy areas, as we do in
% Figure~\ref{fig:confusionRobust8c_zoom}, we see overshoots on the order of 32
% and undershoots on the order of -13, where the exact solution varies between 0
% and 1. The cause of these overshoots and undershoots is a little mystery,
% especially because they don't show up until 8 refinement steps in. We will
% explore this problem a little more when we look at the wedge problem.
% 
% \begin{figure}[h!]
% \centering
% \includegraphics[width=0.6\textwidth]{figs/Confusion/robust8c_zoom.png}
% \caption{Zoomed in conservative skewed convection-diffusion problem after 8
% refinements}
% \label{fig:confusionRobust8c_zoom}
% \end{figure}

Finally, we plot the flux imbalances for the several methods in
Figure~\ref{fig:confusionGraphFlux} and Figure~\ref{fig:confusionRobustFlux}.
Interestingly, it appears the effectiveness of our local conservation
formulation drops as we refine with the graph norm.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/graphFlux.pdf}
\caption{With graph norm}
\label{fig:confusionGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/robustFlux.pdf}
\caption{With robust norm}
\label{fig:confusionRobustFlux}
\end{subfigure}
\caption{Flux imbalance in skewed confusion solutions}
\end{figure}

\subsection{Double Glazing Problem}
This nominal problem definition takes the same unit square domain with 
\[
\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad f=0\,;\quad
\hat u=
\begin{cases}
1 & \mbox{on }\Gamma_{right}\\
0 & \mbox{else }
\end{cases}\,,
\]
except that this definition for the boundary is not legal for $\hat u\in
H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The following
results are for $\epsilon=10^{-2}$. Note that $\bbeta=(0,0)^T$ at the center
of the domain.

The choice of test norm appears to have a small effect on the choice mesh
refinement choices as shown in Figure~\ref{fig:doubleglazing}. Other than
that, the conservative and nonconservative solutions behave almost exactly to
the eye. The flux imbalances in Figure~\ref{fig:doubleglazing_flux} are what
we would expect. The nonconservative formulation appears to become more
conservative with refinement.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graph6c.png}
\caption{Conservative with graph norm}
\label{fig:doubleglazingGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robust6c.png}
\caption{Conservative with robust norm}
\label{fig:doubleglazingRobust6c}
\end{subfigure}
\caption{Double glazing problem after 6 refinements}
\label{fig:doubleglazing}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/graphFlux.pdf}
\caption{With graph norm}
\label{fig:doubleglazingGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/robustFlux.pdf}
\caption{With robust norm}
\label{fig:doubleglazingRobustFlux}
\end{subfigure}
\caption{Flux imbalance in double glazing solutions}
\label{fig:doubleglazing_flux}
\end{figure}

\subsection{Vortex Problem}
This problem models a mildly diffusive vortex convecting fluid in a circle. We
deal with domain $\Omega=[-1,1]^2$ with $\epsilon=10^{-4}$, $\bbeta=(-y,x)^T$,
and $f=0$. Note that $\bbeta=0$ at the domain center. We have an inflow
boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set $\hat
t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
$u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
of boundary edges to 1 at corners. We don't enforce an outflow boundary.

Each of the four methods seems to have it's own specific refinement pattern,
but in general we can see that the nonconservative formulations seem to place
much more refinements in the center of the vortex where the solution is
constant. The conservative formulations seem to recognize that more error is
concentrated on the edges of the vortex where we have a sharp change from
constant values to linear growth in terms of radius. Again we see that
standard DPG appears to approach conservation with refinement, and
unfortunately the conservative formulation appears to be losing enforcement
under the robust norm.

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/graph6nc.png}
\caption{Nonconservative with graph norm}
\label{fig:vortexGraph6nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/robust6nc.png}
\caption{Nonconservative with robust norm}
\label{fig:vortexRobust6nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/graph6c.png}
\caption{Conservative with graph norm}
\label{fig:vortexGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/robust6c.png}
\caption{Conservative with robust norm}
\label{fig:vortexRobust6c}
\end{subfigure}
\caption{Vortex problem after 6 refinements}
\label{fig:vortex}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/graphFlux.pdf}
\caption{With graph norm}
\label{fig:vortexGraphFlux}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/robustFlux.pdf}
\caption{With robust norm}
\label{fig:vortexRobustFlux}
\end{subfigure}
\caption{Flux imbalance in vortex solutions}
\label{fig:vortex_flux}
\end{figure}

\subsection{Wedge Problem}
We devised this problem to examine some of the issues we were having blow up
of the solution under the robust test norm. The domain is a rectangle
$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
of the wedge.

When the colorscale is scaled from 0 to 1, the macro view of all of the
solutions looks nearly identical as seen in Figure~\ref{fig:wedge}. However,
we start to see some differences in the refinement patterns in
Figure~\ref{fig:wedge_mesh} indicating that the various methods distribute
error in different ways. We see more evidence of this when we zoom in on the
tip of the wedge where we get a change in boundary conditions. The graph norm
solutions don't exhibit any significant problems here. The nonconservative and
conservative solutions vary smoothly in the range $(-0.00127, 1.03)$, plus or
minus some less significant digits. The nonconservative robust solution jumps
from -19.6 to 20.3 at the tip, though this appears to be a very localized
phenominon. Adding local conservation appears to exacerbate this situation as
the solution varies from -20.0 to 23.2 and appears to polute a larger area of
the problem. We implemented a crude hp-adaptive refinement strategy in order
to try to resolve any singularities present in the solution. If the cell
measure dips below $5\times10^{-4}$, we switch from h-adaptivity to
p-adaptivity. Figure~\ref{fig:wedge_poly} shows the resultant polynomial
orders after refinement. It really appears that the apparent singularities in
the robust solutions are not physical phenomena that just need resolution, but
a weakness in the method with the robust test norm.

We plot the flux imbalances in Figure~\ref{fig:wedge_flux}. Despite the
extreme overshoots and undershoots in the conservative method with the robust
test norm, we still appear to maintain acceptable levels of conservation.

\begin{figure}
\centering
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c}
\end{subfigure}
\caption{Wedge problem after 16 refinements}
\label{fig:wedge}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_mesh.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc_mesh}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_mesh.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc_mesh}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c_mesh.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c_mesh}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c_mesh.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c_mesh}
\end{subfigure}
\caption{Wedge problem mesh after 16 refinements}
\label{fig:wedge_mesh}
\end{figure}

\begin{figure}
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16nc_zoom.png}
\caption{Nonconservative with graph norm}
\label{fig:wedgeGraph16nc_zoom}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16nc_zoom.png}
\caption{Nonconservative with robust norm}
\label{fig:wedgeRobust16nc_zoom}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/graph16c_zoom.png}
\caption{Conservative with graph norm}
\label{fig:wedgeGraph16c_zoom}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/robust16c_zoom.png}
\caption{Conservative with robust norm}
\label{fig:wedgeRobust16c_zoom}
\end{subfigure}
\caption{Wedge problem zoomed in after 16 refinements}
\label{fig:wedge_zoom}
\end{figure}

>>>>

\subsection{Local Problem}
The optimal test functions are determined by solving local problems determined
by the choice of test norm. We consider several options for the test norm.
The graph norm \cite{DPGOverview} is one of the most natural norms to consider
as it is derived directly from the adjoint of the problem supplemented with
(possibly scaled) $L^2$ field terms to upgrade it from a semi-norm. 
Chan \etal\cite{ChanHeuerThanhDemkowicz2012} derived a more robust alternative
norm for convection diffusion (dubbed the robust norm). We recently
developed a modification of the robust norm that appears to produce better
results in the presence of singularities.

\subsubsection{Robust Norm}
For illustrative purposes we choose the robust
test norm developed by Chan \etal\cite{ChanHeuerThanhDemkowicz2012}. With this
choice, we get our local problem:

@@

\section{Numerical Experiments}
In \ref{sec:problemDescriptions} we define each numerical experiment, and in
\ref{sec:problemAnalysis} we discuss the solution properties in general. We
solve with second order field variables and flux ($u$, $\bsigma$, and $\hat
t$), third order traces ($\hat t$), and fifth order test functions ($v$ and
$\btau$).

Describe how we check local conservation.

\subsection{Description of Problems}\label{sec:problemDescriptions}
Unless otherwise noted, the problem domain is $\Omega=[0,1]^2$ and $f=0$. Also
note that except for the discontinuous source problem, blue corresponds to
$u=0$ and red to $u=1$ with a linear scaling in between.

\subsubsection{Erickson-Johnson Model Problem}
The Erickson-Johnson problem is one of the few convection-diffusion problems
with a known analytical solution. Take 
$\bbeta=(1,0)^T$ and boundary conditions $\hat t=\bbeta\cdot\mathbf{n} u_0$ when
$\beta_n\le0$, where $u_0$ is the trace of the exact solution, and $\hat u=0$
when $\beta_n>0$. For
$n=1,2,\cdots$, let
$\lambda_n=n^2\pi^2\epsilon$,
$r_n=\frac{1+\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$, and 
$s_n=\frac{1-\sqrt{1+4\epsilon\lambda_n}}{2\epsilon}$. The exact solution
is
\begin{equation}
u(x,y)=C_0+\sum_{n=1}^\infty C_n\frac{\exp(s_n(x-1))-\exp(r_n(x-1))}
{r_n\exp(-s_n)-s_n\exp(-s_n)}\cos(n\pi y)\,.
\label{eq:ericksonExact}
\end{equation}
Taking $\epsilon=10^{-2}$, $C_1=1$, and $C_{n\neq1}=0$, the exact solution looks
like Figure \ref{fig:erickson}.

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/Erickson/exact.png}
\caption{Erickson-Johnson exact solution}
\label{fig:erickson}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/Erickson/modifiedError.pdf}
\caption{Error in Erickson-Johnson solutions}
\label{fig:ericksonError}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{figs/Erickson/graphFlux.pdf}
\caption{Flux imbalance in Erickson-Johnson solutions}
\label{ericksonFlux}
\end{figure}

\subsubsection{Skewed Convection-Diffusion Problem}
This is a standard convection-diffusion problem with a skewed convection
vector relative to the mesh. We take $\bbeta=(2,1)$, and on the left and
bottom inflow boundaries we impose $\hat t=1-x-y$ while the right and top
boundaries have $\hat u=0$. We solve for $\epsilon=10^{-4}$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/modified8nc.png}
\includegraphics[width=\textwidth]{figs/Confusion/modified8nc_mesh.png}
\caption{Nonconservative}
\label{fig:confusionModified8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Confusion/modified8c.png}
\includegraphics[width=\textwidth]{figs/Confusion/modified8c_mesh.png}
\caption{Conservative}
\label{fig:confusionModified8c}
\end{subfigure}
\caption{Skewed convection-diffusion problem after 8 refinements}
\label{fig:confusion}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=0.8\textwidth]{figs/Confusion/modifiedFlux.pdf}
\caption{Flux imbalance in skewed convection-diffusion solutions}
\label{fig:confusionFlux}
\end{figure}

\subsubsection{Double Glazing Problem}
This nominal problem definition takes the same unit square domain with 
\[
\bbeta=\binom{2(2y-1)(1-(2x-1)^2)}{-2(2x-1)(1-(2y-1)^2)}\,;\quad
\hat u=
\begin{cases}
1 & \mbox{on }\Gamma_{right}\\
0 & \mbox{else }
\end{cases}\,,
\]
except that this definition for the boundary is not legal for $\hat u\in
H^{\frac{1}{2}}(\Gamma_h)$ which is continuous. Therefore we use a ramp of
width $\sqrt{\epsilon}$ on the right edge to go from 0 to 1. The 
results are for $\epsilon=10^{-2}$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5nc.png}
\caption{Nonconservative}
\label{fig:doubleglazingGraph6c}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/DoubleGlazing/modified5c.png}
\caption{Conservative}
\label{fig:doubleglazingRobust6c}
\end{subfigure}
\caption{Double glazing problem after 5 refinements}
\label{fig:doubleglazing}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/DoubleGlazing/modifiedFlux.pdf}
\caption{Flux imbalance in double glazing problem}
\label{fig:doubleglazingFlux}
\end{figure}

\subsubsection{Vortex Problem}
This problem models a mildly diffusive vortex convecting fluid in a circle. We
deal with domain $\Omega=[-1,1]^2$, with $\epsilon=10^{-4}$, and
$\bbeta=(-y,x)^T$. Note that $\bbeta=\mathbf{0}$ at the domain center. We have an
inflow boundary condition when $\bbeta\cdot\mathbf{n}<0$, in which case we set
$\hat t=\bbeta\cdot\mathbf{n}\cdot u_0$ where
$u_0=\frac{\sqrt{x^2+y^2}-1}{\sqrt{2}-1}$ which will vary from 0 at the center
of boundary edges to 1 at corners. We don't enforce an outflow boundary.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/modified6nc.png}
\caption{Nonconservative}
\label{fig:vortexModified6nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Vortex/modified6c.png}
\caption{Conservative}
\label{fig:vortexModified6c}
\end{subfigure}
\caption{Vortex problem after 6 refinements}
\label{fig:vortex}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/Vortex/modifiedFlux.pdf}
\caption{Flux imbalance in vortex solutions}
\label{fig:vortex_flux}
\end{figure}

\subsubsection{Wedge Problem}
We devised this problem to examine some of the issues we were having blow up
of the solution under the robust test norm. The domain is a rectangle
$[-0.5,0.5]\times[-1,0.5]$ where the triangle connecting the bottom edges with
the origin at $(0,0)$ is removed. The convection vector $\bbeta=(1,0)^T$,
$\epsilon=10^{-1}$, and we apply boundary conditions $\hat t=0$ on the left
inflow edge, $\hat u=0$ on the top edge, $\bbeta\cdot\mathbf{n}\cdot\hat
u-\hat t=\sigma_n=0$ on the right outflow edge, $\hat u=1$ on the leading edge
of the wedge, and $\hat t=\bbeta\cdot\mathbf{n}\cdot 1$ on the trailing edge
of the wedge.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/modified16nc.png}
\includegraphics[width=\textwidth]{figs/Wedge/modified16nc_mesh.png}
\caption{Nonconservative}
\label{fig:wedgeGraph16nc}
\end{subfigure}
\begin{subfigure}[t]{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Wedge/modified16c.png}
\includegraphics[width=\textwidth]{figs/Wedge/modified16c_mesh.png}
\caption{Conservative}
\label{fig:wedgeRobust16nc}
\end{subfigure}
\caption{Wedge problem after 16 refinements}
\label{fig:wedge}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/Wedge/modifiedFlux.pdf}
\caption{Flux imbalance in wedge solutions}
\label{fig:wedge_flux}
\end{figure}

\subsubsection{Inner Layer Problem}
In this problem, $\bbeta=(\frac{\sqrt{3}}{2},\frac{1}{2})^T$ and we have a
discontinuous flux inflow condition where $\hat t=0$ if $y\le0.2$ and $\hat
t=\bbeta\cdot\mathbf{n}$ if $y>0.2$. On the outflow, $\hat u=0$. We use a very
small diffusion scale of $\epsilon=10^{-6}$ which creates a very thin inner
layer.
% Nonconservative solution in range $[-0.38, 1.34]$.
% Conservative solution in range $[-0.39, 1.38]$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8nc_mesh.png}
\caption{Nonconservative}
\label{fig:innerlayer8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c.png}
\includegraphics[width=\textwidth]{figs/InnerLayer/modified8c_mesh.png}
\caption{Conservative}
\label{fig:innerlayer8c}
\end{subfigure}
\caption{Inner layer problem after 8 refinements}
\label{fig:innerlayer}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/InnerLayer/modifiedFlux.pdf}
\caption{Flux imbalance in inner layer solutions}
\label{fig:innerlayer_flux}
\end{figure}

\subsubsection{Discontinuous Source Problem}
Here, $\bbeta=(0.5,1)^T/\sqrt{1.25}$, and we have a discontinuous source term
such that $f=1$ when $y\ge2x$ and $f=-1$ when $y<2x$. We apply boundary
conditions of $\hat t=0$ on the inflow and $\hat u=0$ on the outflow. Contrary
to the other problems discussed, the solution for this problem does not range
from 0 to one. Rather, the colorbar in Figure \ref{fig:discontinuous} is
scaled to  $[-1.110,0.889]$.

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/graph8nc.png}
\caption{Nonconservative}
\label{fig:discontinuousModified8nc}
\end{subfigure}
\begin{subfigure}[t]{0.45\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Discontinuous/robust8nc.png}
\caption{Conservative}
\label{fig:discontinuousModified8c}
\end{subfigure}
\caption{Discontinuous source problem after 8 refinements}
\label{fig:discontinuous}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/Discontinuous/modifiedFlux.pdf}
\caption{Flux imbalance in discontinuous source solutions}
\label{fig:discontinuous_flux}
\end{figure}

\subsubsection{Hemker Problem}
The Hemker problem is defined on a domain
$\Omega=\{[-3,9]\times[-3,3]\}\setminus\{(x,y):x^2+y^2<1\}$, essentially a simplified
model of flow past an infinite cylinder. We start with the initial mesh shown
in Figure~\ref{fig:hemkerInitial} in which we approximate the circle by 8
fourth order curvilinear polynomial segments. As we refine, the new elements are
fitted to better approximate an exact circle.The boundary conditions are $\hat
t=\bbeta\cdot\mathbf{n}\cdot 1$ on the left inflow boundary,
$\bbeta\cdot\mathbf{n}\cdot\hat u-\hat t=\sigma_n=0$ on the right outflow
boundary, $\hat t=0$ on the top and bottom edges, and $\hat u=1$ on the
cylinder.

\begin{figure}[p]
\centering
\includegraphics[width=0.8\textwidth]{figs/Hemker/initial_mesh.png}
\caption{Initial mesh for the Hemker problem}
\label{fig:hemkerInitial}
\end{figure}

\begin{figure}[p]
\centering
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8nc.png}
\end{subfigure}
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8nc_mesh.png}
\caption{Nonconservative}
\label{fig:hemkerModified8nc}
\end{subfigure}
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8c.png}
\end{subfigure}
\begin{subfigure}[t]{0.6\textwidth}
\centering
\includegraphics[width=\textwidth]{figs/Hemker/modified8c_mesh.png}
\caption{Conservative}
\label{fig:hemkerModified8c}
\end{subfigure}
\caption{Hemker problem after 8 refinements}
\label{fig:hemker8}
\end{figure}

\begin{figure}[p]
\centering
\centering
\includegraphics[width=0.8\textwidth]{figs/Hemker/modifiedFlux.pdf}
\caption{Flux imbalance in Hemker problem}
\label{fig:hemkerFlux}
\end{figure}

\subsection{Analysis of Results}\label{sec:problemAnalysis}
% Solution quality
The general trend we see looking at the results is that the solution quality
of the conservative and conconservative formulations is nearly identical. This
is ideal, as we wish to preserve the attractive features of DPG --
namely that it minimizes error in the energy norm. In particular, when we
examine the error convergence plots for the Erickson-Johnson problem, the
energy levels for the two methods lie nearly right on top of each other. This
seems to indicate at the least that enforcing local conservation doesn't hurt
DPG too much.

% Overshoots/undershoots
Another measure of solution quality is to look at the magnitude of overshoots
and undershoots in the solution. In most of the problems considered (barring
the discontinuous source problem) the exact solution would range exactly
between 0 and 1. The the resolved solutions, the divergence from these values
would be negligible, but for the inner layer, in which $\epsilon=10^{-6}$, we
get overshoots and undershoots along the separation line. For the
nonconservative formulation, the solution range for $u$ was $[-0.392,1.342]$,
while the conservative solution range was $[0.389,1.378]$. This difference is
easily accounted for by the differences in refinement patterns between the two
methods.

% Mesh refinements
It is clear when comparing the refinement patterns that the two methods appear
to calculate slightly different error representation functions (which
determine which elements to adaptively refine). Standard DPG minimizes the
error in the energy norm, but the Lagrange multipliers in the conservative
formulation shift the solution slightly. So we should see somewhat higher
error and different elements will get chosen for refinement. The choice of
test norm also plays into this calculation of the error representation
function. As discussed earlier, the conservative formulation allows us to
throw away the $L^2$ term on $v$. The inclusion of this term required certain
assumptions on $\bbeta$ \cite{ChanHeuerThanhDemkowicz2012} that break down for
the vortex problem. Here we see the nonconservative method needlessly refine
in the center of the domain where the solution is constant. The conservative
scheme is more discerning about refinements and focuses refinements where
solution features are changing. In general, though, both methods appear to
follow very similar refinement patterns.

% Mass conservation
It shouldn't come as a surprise that the conservative and nonconservative
solutions match each other so closely. The conservative formulation
enforces local conservation more strictly, but if we examine the flux
imbalance plots, the nonconservative formulation is nearly conservative on its
own -- and appears to become more conservative with refinement. The flux
imbalance of the conservative methods appears to bounce around close to the
machine epsilon (plus a few orders of magnitude). The level of enforcement
appears to creep up with more degrees of freedom, indicating possible
accruement of numerical error.
